---
title: "DS 613 Homework 2"
author: "Xuehao Wang"
date: "02/15/2021"
output:
  word_document: default
  html_notebook: default
---

1) Enter and run USArrests. What type of information is shown in the data table USArrests?  (Three or four sentences)
```{r}
USArrests
```
There are five column in the table, first one is state name, which is character, the rest four are all type of double and integer.

2) Use and show R coding that features a map function to show maximum values for all variables of the USArerests data frame.  Which State has the largest number of Assaults according to the USAressts data frame?
```{r}
library(tidyverse)
library(dplyr)

map_dbl(USArrests, max)

USArrests %>% 
  filter(Assault == 337) #North Carolina has the largest number of Assaults according
```

3) Install the nycflights13 package: install.packages("nycflights13") , call the following library:  library(nycflights13), and then enter flights (this will produce the flights data table)
```{r}
library(nycflights13)
flights
```

4) Use and show R code that will indicate how many rows and how many columns the flights data has.  Review and revisit your notes from STAT 412/612.  Describe a tibble (two or three sentences). Now use and show R code that verifies that flights is a tibble
```{r}
nrow(flights)
ncol(flights)
class(flights)
```
tibble is data frame in R programming language, it contains different type of variable in the tibble

5) Now Use and show R code (featuring a map function) that will output the type of each column of the flights tibble.
```{r}
map(flights, typeof)
```

6)  Use and show R coding that features usage of a map function to find the slope and the intercept of models for the different levels of the Species variable of the iris data frame.  For each model, Sepal.Width predicts Sepal.Length.
```{r}
iris %>% 
  split(.$Species) %>% 
  map(~lm(Sepal.Length ~ Sepal.Width, data = .))
```

7)
```{r}
V <- list(12, 22, 27, 31.5, NA, 39, "east")
V
```

For the given list above;
7a) Use and show R code to find the length of the list
```{r}
length(V)
```

7b) Use and show R code that will extract the missing value
```{r}
V[is.na(V)]
```

7c) Use and show R code that will extract the third object
```{r}
V[3]
```

7d) Use and show R code that will extract the character string and the minimum number.
```{r}
V[c(1,7)]
```

7e) Use one line of code to show that the seventh object is a character object.
```{r}
str(V[[7]])
```
